Glyph-maps for visualizing climate data and models

### 2011-08-25 paper.tex
tweaking intro

In this paper we explore the use of a different type of display, that uses icons on the map. Icon plots date back to the star glyphs of  \citep{kleiner}, made infamous by \citep{Chernoff}. They are used, infrequently to examine multivariate data.

>>>>

In this paper we explore the use of a different type of display, that uses icons on the map, for climate data. Icon plots date back to the star glyphs of  \citep{kleiner}, made infamous by \citep{Chernoff}. They are used, infrequently, to examine multivariate data. An icon is produced by mapping each variable to some feature of the icon. One icon is generated for every case in the data set. For large data sets it is infeasible to digest the quantity of icons, and for multivariate data there is no natural order so it can be like having a mountain of little stamps to rearrange and organize, in order to understand the structures present in the data. For spatiotemporal data ordering icons is naturally done by spatial location. There is also usually some spatial trend, or continuity, which will make digesting patterns among the icons simpler.
